---
title: "Data Analytics II: Project Part A"
author: |
    | E
    | your names here
    | your reg numbers here
date: "2021-XX-XX"
output: pdf_document
df_print: paged
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load needed libraries here

```

## A.1 - Explorative Data Analysis (EDA)


```{r A.1.i}

```

Make your comments here

```{r A.1.ii}

```

Make your comments here

```{r A.1.iii}

```

How did you construct your histograms? 

Do the variables income and age appear to be (approximately) normally distributed? 

Can you think of a suitable distribution for the variable children? 


## A.2 - Confidence Intervals


```{r A.2.i}

```

Make your comments here

```{r A.2.ii}

```

Make your comments here

```{r A.2.iii}

```

Are the underlying assumptions for calculating such an interval satisfied for the current data? 

## A.3 - Confidence Intervals and the Sample Size

```{r A.3.i}

```

what is the required sample size?

```{r A.3.ii}

```

Why it is costly to improve the ME by one unit? 

Is the cost worth it compared to the improvement we gain?

```{r A.3.iii}

```

Make your comments here

What changes should be made to the confidence level as the size of the same increases? 

What are the effects of doing this on our analysis?

## A.4 - Confidence Intervals: Comparison of Population Means

```{r A.4.i}

```

Are there any differences in the income variable for the segments “Travelers” and “Urban Hip”? 

What are the underlying assumptions used to calculate this interval?

Are they coherent with the current data? 
